Enhancement of SDR in Thessaloniki

### 2024-06-06 GHI_enh_03_process.tex
Commit 2024-06-04 19:13
Commit 2024-06-05 19:11
Commit 2024-06-05 21:10
Commit 2024-06-06 14:14

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-22}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
Alpha * HAU is CS\_ref

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-2} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-3} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-4} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-5} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-6} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-7} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-8} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-9} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-10} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-11} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-12} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20} \end{center}

@@

\begin{verbatim}
2024-05-22 09:38:39.3 athan@tyler GHI_enh_03_process.R 5.198113 mins
\end{verbatim}

>>>>

\usepackage{float}

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-06}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
    0.0    89.7   180.0   180.0   270.3   360.0 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.5835   0.6886   0.3233  28.1502  83.4876 
\end{verbatim}

Alpha * HAU is CS\_ref

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-1}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-1}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-2}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-2}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-3}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-3}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-4}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-4}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-5}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-5}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-6}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-6}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-7}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-7}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-8}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-8}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-9}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-9}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-10}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-10}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-11}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-11}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-12}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-12}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-13}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-14}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-15}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-16}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-17}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-18}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-19}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-6-20}
\end{figure}

@@

\begin{verbatim}
2024-06-06 10:26:55.1 athan@tyler GHI_enh_03_process.R 5.853366 mins
\end{verbatim}
